The proposed algorithm works off the key assumption for future biomedical hyperspectral images that the eye tissues of interest lie in spatially coherent regions and that pixels near each other share similar spectral characteristics. At the heart, a segmentation approach aims to minimize inter segment variance and maximize intrasegment variance. In the context of hyperspectral imaging, the goal of creating accurate segmentations and maximizing accuracy are often the same. As to efficiency directly, the pre clustering step is crucial to allowing an efficient implementation of the graph approach to segmentation. The relaxed normalized cuts approach we implement operates in near cubic time complexity, by selecting a certain average pixel to superpixel ratio, the running time of the algorithm is reduced cubically with respect to a graph approach without superpixel generation.

The experimental results on real-world satellite hyperspectral datasets demonstrate the effectiveness of the proposed approach. It achieves a high degree of accuracy in material identification while having a high degree of flexibility in terms of choices on parameters to produce the final segmentation output. This method offers a valuable tool for researchers and practitioners working in diverse fields that utilize hyperspectral imaging technology in unlabelled scenarios, such as remote sensing and biomedical hyperspectral imaging. Future research directions would be to explore different constructions of the spatial-spectral affinity matrix presented in \eqref{nc:spatial-spectral-mtx}. While the spectral angle metric is useful in many hyperspectral scenarios, the argument can be made that spectral angle alone cannot capture the intricate differences between normalized spectra for certain fields of study, and instead, a mixed of different measures must be considered.

In conclusion, this work presented a novel graph-based segmentation approach that effectively addresses the challenges associated with blind segmentation in hyperspectral images. The proposed method leverages the strengths of both spectral similarity and spatial proximity to achieve accurate segmentation while maintaining computational efficiency. By incorporating the estimated abundance information as a supportive feature, the algorithm refines the segmentation process, leading to superior results in both accuracy and efficacy.
